Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-05-28 snapshot_system/design1.tex
ew

>>>>

{\bf Snapshot Representation}.
The virtual device driver uses a bitmap to track the changes 
that have been made to virtual disk.
Every bit in the bitmap represents a fix-sized (2MB) region called \textit{segment}, indicates whether the segment
is modified since last backup. Hence we could treat segment as the basic unit in snapshot backup similar to
file in normal backup: a snapshot could share a segment with previous snapshot it is not changed. 
Moreover, we break 
segments into var-sized chunks (average 4KB) using content-based chunking algorithm,
which brings the opportunity of fine-grained deduplication by
allowing data sharing between segments.

\begin{figure}[htbp]
  \centering
  \epsfig{file=images/snapshot_representation.eps, width=3.7in}
  \caption{An example of snapshot representation.}
  \label{fig:snapshot}
\end{figure}
As a result, the representation of each snapshot is designed as a two-level index data structure 
in the form of a hierarchical directed acyclic graph as shown in Figure \ref{fig:snapshot}.
A snapshot recipe contains a list of segments, each of which is represented as a segment recipe
that holds the meatdata of its chunks. We choose this two-level structure because in practice we
observe that during each backup period only a small amount of VM data are added or modified. 
As the result, even the metadata of two snapshots can be highly similar, 
thus aggregating a large number of chunks as one segment can significantly reduce the space cost of snapshot metadata.
Furthermore, instead of using variables-sized segments, we use a dirty bit to capture the change status of fix-sized
segments which greatly ease the segment-level deduplication.

In both two kind of recipes, 
they do not include the actual data but only have
 references point to the data which are either stored in append store or CDS.
In our implementation the data reference is a 8 bytes field which is either an 
ASID (discuss in \ref{sect:append} or an offset of 
An additional flag indicates

### 2013-05-28 snapshot_system/snapshot.tex
ew

{\bf Snapshot Representation}.
The virtual device driver uses a bitmap to track the changes 
that have been made to virtual disk.
Every bit in the bitmap represents a fix-sized (2MB) region called \textit{segment}, indicates whether the segment
is modified since last backup. Hence we could treat segment as the basic unit in snapshot backup similar to
file in normal backup: a snapshot could share a segment with previous snapshot it is not changed. 
Moreover, we break 
segments into var-sized chunks (average 4KB) using content-based chunking algorithm,
which brings the opportunity of fine-grained deduplication by
allowing data sharing between segments.

\begin{figure}[htbp]
  \centering
  \epsfig{file=images/snapshot_representation.eps, width=3.7in}
  \caption{An example of snapshot representation.}
  \label{fig:snapshot}
\end{figure}
As a result, the representation of each snapshot is designed as a two-level index data structure 
in the form of a hierarchical directed acyclic graph as shown in Figure \ref{fig:snapshot}.
A snapshot recipe contains a list of segments, each of which is represented as a segment recipe
that holds the meatdata of its chunks. We choose this two-level structure because in practice we
observe that during each backup period only a small amount of VM data are added or modified. 
As the result, even the metadata of two snapshots can be highly similar, 
thus aggregating a large number of chunks as one segment can significantly reduce the space cost of snapshot metadata.
Furthermore, instead of using variables-sized segments, we use a dirty bit to capture the change status of fix-sized
segments which greatly ease the segment-level deduplication.

In both two kind of recipes, 
they do not include the actual data but only have
 references point to the data which are either stored in append store or CDS.
In our implementation the data reference is a 8 bytes field which is either an 
ASID (discuss in \ref{sect:append} or an offset of 
An additional flag indicates

>>>>

This section analyzes the choice of popular blocks and its impact on the deduplication efficiency.
It also  compares the  fault resilience of our VM-centric deduplication approach with a standand approach using 
global deduplication.

{\bf Impact of CDS deduplication.}
Our empirical study based on VM images from production environment\cite{ieeecloud} showed that the
frequency of data duplication follows Zipf-like distribution\cite{zipf},
with the exponent $\alpha$ between 0.65 ~ 0.70.
As a result, it can be proved that deduplication efficiency of CDS index is scalable:

[Describe the dedup efficiency model in detail]
Let $S_c$ be the total number of FPs in CDS, $S_g$ be the total number of FPs in global index, $F$ be the size of a FP, $N$ be the number of nodes in the cluster, $m$ be the memory on each node that are used by CDS, $D$ be the amount of data on each node, and $B$ be the average block size. The deduplication efficiency will be:
\begin{equation}
  E = (S_c / S_g)^{1-\alpha}
\end{equation}
The $S_c$ and $S_g$ can be expressed as:
\begin{equation}
S_c = N*m/F, S_g = N*D/B
\end{equation}
By replacing $S_c$ and $S_g$ in the first formula, we have:
\begin{equation}
  E = (\frac{m*B}{F*D})^{1-\alpha}
\end{equation}

Since $B$, $D$ and $F$ are pre-configured constants, the deduplication efficiency of CDS is only controlled by the its memory usage.

{\bf Fault resilence.}
